Downward shortwave solar irradiance enhancement by clouds.

### 2024-05-16 article/article.Rmd
Commit 2024-05-16 19:19

@@

<!-- Lookup table -->
To create a look-up table that aligns with our dataset, we applied some adjustments.
To account for the Sun's variability, in our one-minute GHI measurements, 
we adapted each modeled value by scaling the  
model's input spectrum integral, to the corresponding total solar irradiance (TSI)
provided by NOAA [@Coddington2005].  
Also, we applied the effect of the Earth -- Sun
distance on the irradiance, by using the distance calculated by the Astropy
[@AstropyCollaboration2022] software library. As needed, we interpolate the resulting
irradiances to the exact SZA of our measurements.  For each period of the year, we
used the appropriate atmospheric profile (afglms or afglmw).  Finally, we calculated
the clear sky irradiance value at the horizontal plane.  Thus, we were able to
emulate different atmospheric condition and levels of atmospheric clearness for the
climatological conditions of the site.  With this method, the modeled clear sky
irradiances can be directly compared to each measured one-minute value of GHI, for
different conditions of atmospheric clearness.

>>>>

### Climatology of clear sky irradiance

@@

<!-- Lookup table -->
To create a look-up table, that aligns with our dataset, we applied some adjustments.
To account for the Sun's variability, in our one-minute GHI measurements, we adapted
each modeled value by scaling the model's input spectrum integral, to the
corresponding total solar irradiance (TSI) provided by NOAA [@Coddington2005].  Also,
we account for the effect of the Earth -- Sun distance on the irradiance, by using
the distance calculated by the Astropy [@AstropyCollaboration2022] software library.
As needed, we interpolate the resulting irradiances to the exact SZA of our
measurements.  For each period of the year, we used the appropriate atmospheric
profile (afglms or afglmw).  Finally, we calculated the clear sky irradiance value at
the horizontal plane.  Thus, we were able to emulate different atmospheric condition
and levels of atmospheric clearness for the climatological conditions of the site.
With this method, the modeled clear sky irradiances can be directly compared to each
measured one-minute value of GHI, for different conditions of atmospheric clearness.

### Long term change of clear sky irradiance

<!-- Aerosol change -->
The above clear sky reference values are not enough to describe the long term
variation due to the changes of the atmospheric constituents. As observed
by @Natsis2023, there is long term brightening effect, over Thessaloniki for the
studied period. In order to better describe this change, we used, estimations of AOD
change derived from two sources. For 1993 -- 2005, @Kazadzis2007 have found a change
of $-3.8\,\%$ per year at AOD on $340$ nm, using a Brewer spectrophotometer. For 2005
to 2023, we derived the trend from the available AERONET data.

To create a unified trend for the long term change of the clear sky irradiance, we
sim simulated
